
\input{00preamble}

\begin{document}

\input{00typein_new}

%=======================タイトルページ（表紙）==================

\title{{\color{dominant} \Huge \nyuryokua} \\ {\large \nyuryokub}}
\date{\nyuryokuc}
\author{\color{dominant}\sffamily \bfseries Shirokane CPA Firm}

\begin{titlepage}

\title{{\color{dominant} \Huge \nyuryokua} \\ {\large \nyuryokub}}
\date{\nyuryokuc}
\author{\color{dominant}\sffamily \bfseries Shirokane CPA Firm}

\maketitle  %HPテンプレート用にタイトルページの出力

\end{titlepage}

%=======================ヘッダー部================

\lhead{}  %ヘッダー左側を非表示にするため。%で機能停止すれば、章立てが表示される。
\rhead{\color{dominant} \nyuryokuc \ \ \ P.\ \thepage / \pageref{LastPage}}

\cfoot{}  %ページ底中央を非表示するため。%で機能停止すれが、ページ数が表示される。
\rfoot{\color{dominant} \sffamily \bfseries \href{http://www.shirokanecpa.com/}{http://www.shirokanecpa.com/} \\ \copyright 2025 Shirokane CPA Firm}

%=======================表題部==================

\vspace*{-20mm}
\begin{center}
\part*{\nyuryokud}
\end{center}
\vspace{15mm}

%\begin{table}[h]
%  \begin{tabular}{lcl}
%    To & : & \nyuryokue \\
%        &   & \nyuryokuee \\
%    From & : & \nyuryokuf \\
%    Subject & : & \nyuryokug \\
%    Date & : & \nyuryokuh \\
%  \end{tabular}
%\end{table}

 \renewcommand{\headrulewidth}{11pt}% secondgreen Line
 \hbox to 120mm{%
 \color{dominant} \leaders\hrule height11pt\hfil}

%=====================目次=======================

\vspace{18mm}
{\color{dominant} \LARGE \bfseries Contenets}
\vspace{-5mm}
\setcounter{tocdepth}{2}
\tableofcontents
\clearpage

%======================本文部分（以下を作成）======
\vspace{-20pt}


%会社種類の選択について
\section{Deciding on the type of company}

\begin{coloritemize}
\item We can support to establish all of the following entities.
 \begin{itemize}
 \item Kabushiki Kaisha (hereinafter KK, similar to Corporation in the U.S. and Public Limited Company in the G.B.)
 \item Godo Kaisha (hereinafter GK, similar to Limited Liability Company in the U.S. and Limited Liability Partnership in the G.B. but GK does not use pass-through taxation.)
 \item Gomei Kaisha
 \item Goshi Kaisha
 \item Ippan Shadan Hojin (hereinafter ISH, similar to Nonprofit Corporation in the U.S. and Company Limited by Guarantee in the G.B. but ISH activities are not limited to non-profit endeavors; they can also include commercial activities (businesses).)
 \item Ippan Zaidan Hojin (hereinafter IZH)\footnote{Ippan Zaidan Hojin is created through the endowment more than JPY 3M) of assets by a founder. These assets are legally separated from the founder and must be used in accordance with the foundation’s stated purpose.}
 \end{itemize}
\item The process of establishing a company that offers legal protection to investors and can operate on a large scale is rigorous and, therefore, expensive.
\item KK is recommended.
\end{coloritemize}

Those are four types of corporations stipulated in the Japanese ``Companies Act'': KKs, GKs, Gomei Kaisha (general partnership companies), and Goshi Kaisha (limited partnership companies). In addition, there are Ippan Shadan Hojin and Ippan Zaidan Hojin under the ``Act on General Incorporated Associations and General Incorporated Foundations''.

\subsection{Target of incorporation services}
We can support the establishment of any of those, but the comanies that can be used for business are KKs and GKs, which can realize indirect limited liability.

ISHs are used when the purpose is membership activities, etc., or when used for business schemes.

\subsection{Different establishment procedures}
The incorporation procedures differ depending on the type of company. As a result, the complexity of the documents and procedures to be prepared for the establishment application differs, and the costs of registration and license taxes, etc. also differ.

The establishment procedures for KK and Ippan-Zaidan-Hojin, where ownership and management are legally separated, are complex.

\section{Recommended company}
If the purpose is business, we recommend KK. GKs are usually used as investment vehicles and family-run businesses, and GKs may not be able to gain sufficient credit. In addition, GKs will fail the screening for opening a bank account after the company is established these days.

A KK can be established with a single shareholder. It can also have just one director and no employees.

If your business activities qualify for an ISH, we recommend establishing one. However, in practice, we believe this is often not the case.

\clearpage
\input{aboutme3}





\end{document}

%=======テンプレ======

\section{}
\subsection{}

\begin{coloritemize}
\begin{spacing}{0.95}
  \item 
  \item 
  \item 
  \item 
%  \item 
\end{spacing}
\end{coloritemize}

%======右側折り返しの表（タイトル4文字のケース）28文字を調整して利用======
\begin{table}[h]
  \begin{tabular}{lcp{28em}}
    氏名 & : & Giovvani Pellone, ジォバニ・ペローネ \\
    住所 & : & 東京都目黒区上目黒3-12-23-308 \\
    生年月日 & : & 1964年7月18日 \\
    国籍 & : & イタリア \\
    VISA & : & 就労制限なし \\
    結婚 & : & 既婚（日本人） \\
    職業 & : & 工業デザイナー、クリエイティブ・ディレクター、グラフィック・デザイナー \\
  \end{tabular}
\end{table}

%======表
\begin{minipage}{120mm}
  \begin{tabular}{llll}
\hline
 事業の種類   & 主な収入 & 会計納税単位 & 備考 \\
\hline
  Airbnb事業 & ホストからの手数料収入 & 一般財団法人 & 地域活性化という公共性強調 \\
  ピザ屋 & 飲食店売上 & 株式会社\footnote{当初はアメリカン・ダイナーと同一法人で事業を開始し、後にアメリカン・ダイナーの会社を設立し、必要資産を営業譲渡する方法も考えられます。} & 初期投資が必要、従業員あり \\
  アメリカン・ダイナー & 飲食店売上 & 株式会社 & 初期投資が必要、従業員あり \\
  ヨガ・スタジオ事業 & レッスン料収入 & 個人事業主 & 河辺家の節税目的 \\
  河辺さん個人 & 一般財団法人からの給与所得 & 個人事業主 & \\
  & 飲食会社からの役員報酬 &  & \\
  \hline
  \end{tabular}
\end{minipage}